---
title: "Figure4_TransferClustering"
author: "Fabienne Rössler"
date: '2023-03-24'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning = FALSE}
source("../DLCAnalyzer_Functions_v4.R")
source("../UnsupervisedAnalysis_Functions.R")
library(sp)         #tested with v1.3-2
library(imputeTS)   #tested with v2.7
library(ggplot2)    #tested with v3.1.0
library(ggmap)      #tested with v3.0.0
library(data.table) #tested with v1.12.8
library(cowplot)    #tested with v0.9.4
library(corrplot)   #tested with v0.84
library(keras)      #REQUIRES TENSORFLOW INSTALL. tested with v2.2.5.0
library(readr)
library(tidyr)
library(biganalytics)
library(M3C)
library(stringr)
library(reticulate)
set.seed(123)
```

# Figure 4

```{r}
US <- readRDS("../../data/US_AllData_25Clusters.rds")
```

```{r}
US2 <- SplitUSData(US,select = US$meta$Experiment %in% c("CRS"))
US2 <- TwoGroupAnalysis(US2,group = US2$meta$Condition, lab = "kmeans.25")

US3 <- SplitUSData(US,select = US$meta$Experiment %in% c("DREADD"))
US3 <- TwoGroupAnalysis(US3,group = US3$meta$Treatment, lab = "kmeans.25")

US_comb <- SplitUSData(US,select = US$meta$Experiment %in% c("CRS", "DREADD"))

US_all <- SplitUSData(US, select = US$meta$Session %in% c("CRS1","PostCSI","FST45min","PostYoh","DREADD"))
US_all <- SplitUSData(US_all, omit = names(US_all$files)[US_all$meta$Condition == "Tunnel"] )
```

## Average behavior flow for controls from original data (CSI, FST and Yohimbine)

```{r, fig.width=5, fig.height=5}
A <- US$meta$Session == "PostCSI" & US$meta$Condition == "Control"
B <- US$meta$Session == "PostYoh" & US$meta$Condition == "Control" & US$meta$Treatment == "Saline"
C <- US$meta$Session == "FST45min" & US$meta$Treatment == "Control"

PlotBehaviorFlow(US, lab = "kmeans.25",file = names(US$files)[A|B|C])

pdf("../../Plots/Figure4_behaviorFlow_original.pdf", height = 5, width = 5)
PlotBehaviorFlow(US, lab = "kmeans.25",file = names(US$files)[A|B|C] )
dev.off()
```


## Average behavior flow for controls from transfer data (CRS and DREADD)

```{r, fig.width=5, fig.height=5}
D <- US$meta$Session == "DREADD" & US$meta$Treatment == "saline"
E <- US$meta$Session == "CRS1" & US$meta$Condition == "Control"

PlotBehaviorFlow(US, lab = "kmeans.25",file = names(US$files)[D|E])

pdf("../../Plots/Figure4_behaviorFlow_transfer.pdf", height = 5, width = 5)
PlotBehaviorFlow(US, lab = "kmeans.25",file = names(US$files)[D|E])
dev.off()
```

## Barplots for CRS and DREADD

### CRS

```{r, fig.height=2, fig.width=5.4}
pdat <- US2$Report$kmeans.25
pdat <- data.frame(filename = rownames(pdat),pdat)
pdat <- gather(pdat,key = "key",value = "value", -filename)
pdat$value[is.na(pdat$value)] <- 0
pdat$type <- unlist(lapply(pdat$key,FUN = function(x){strsplit(x, split = "\\.")[[1]][2]}))
pdat$Cluster <- unlist(lapply(pdat$key,FUN = function(x){strsplit(x, split = "\\.")[[1]][1]}))
pdat$Cluster <- as.integer(unlist(lapply(pdat$Cluster,FUN = function(x){strsplit(x, split = "X")[[1]][2]})))
assign <- match(pdat$filename, US2$meta$filename)
pdat$Group <- US2$meta$Condition[assign]
pdat$value <- ifelse(pdat$type == "nframes",pdat$value / 25, pdat$value)
pdat$type[pdat$type == "nframes"] <- "time"
pdat <- pdat[pdat$type == "count",]
df <- aggregate(pdat$value,by = list(pdat$Cluster, pdat$type, pdat$Group), FUN = mean)
colnames(df) <- c("Cluster","type","Group","Mean")
df$SEM <- aggregate(pdat$value,by = list(pdat$Cluster, pdat$type, pdat$Group), FUN = sd)$x / sqrt(16)


p1 <- ggplot(df, aes(x=Cluster, y=Mean, fill=Group, width = 0.75)) + 
  geom_bar(stat="identity", color="black", 
           position=position_dodge()) +
  scale_fill_manual(values = c("white","#009E73")) +
  geom_errorbar(aes(ymin=Mean-SEM, ymax=Mean+SEM), width=.2,
                position=position_dodge(.8)) +
  #geom_point(data = pdat, aes(Cluster, value, color = Group), position = position_jitterdodge(.3), color = "black", alpha = 0.2, size = 0.3)+ 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
  scale_x_continuous(breaks = c(1:25)) +
  facet_wrap(~type, ncol = 1,scales = "free")

print(p1)

pdf("../../Plots/Figure4_barplot_CRS.pdf", height = 2, width = 5.4)
print(p1)
dev.off()

US2$Results[[1]]$Statistics$kmeans.25

cluster_stats <- US2$Results[[1]]$Statistics$kmeans.25
cluster_stats_updated <- cluster_stats[grep("count", cluster_stats$name), ]
cluster_stats_updated$FDR <- p.adjust(cluster_stats_updated$p, method = "BY")
cluster_stats_updated
```

### DREADD

```{r, fig.height=2, fig.width=5.25}
pdat <- US3$Report$kmeans.25
pdat <- data.frame(filename = rownames(pdat),pdat)
pdat <- gather(pdat,key = "key",value = "value", -filename)
pdat$value[is.na(pdat$value)] <- 0
pdat$type <- unlist(lapply(pdat$key,FUN = function(x){strsplit(x, split = "\\.")[[1]][2]}))
pdat$Cluster <- unlist(lapply(pdat$key,FUN = function(x){strsplit(x, split = "\\.")[[1]][1]}))
pdat$Cluster <- as.integer(unlist(lapply(pdat$Cluster,FUN = function(x){strsplit(x, split = "X")[[1]][2]})))
assign <- match(pdat$filename, US3$meta$filename)
pdat$Group <- US3$meta$Treatment[assign]
pdat$value <- ifelse(pdat$type == "nframes",pdat$value / 25, pdat$value)
pdat$type[pdat$type == "nframes"] <- "time"
pdat <- pdat[pdat$type == "count",]
df <- aggregate(pdat$value,by = list(pdat$Cluster, pdat$type, pdat$Group), FUN = mean)
colnames(df) <- c("Cluster","type","Group","Mean")
df$SEM <- aggregate(pdat$value,by = list(pdat$Cluster, pdat$type, pdat$Group), FUN = sd)$x / sqrt(8)

df$Group <- factor(df$Group, levels = c("saline", "cloz"))

p1 <- ggplot(df, aes(x=Cluster, y=Mean, fill=Group, width = 0.75)) + 
  geom_bar(stat="identity", color="black", 
           position=position_dodge()) +
  scale_fill_manual(values = c("white","#E69F00")) +
  geom_errorbar(aes(ymin=Mean-SEM, ymax=Mean+SEM), width=.2,
                position=position_dodge(.8)) +
  #geom_point(data = pdat, aes(Cluster, value, color = Group), position = position_jitterdodge(.3), color = "black", alpha = 0.2, size = 0.3)+ 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
  scale_x_continuous(breaks = c(1:25)) +
  facet_wrap(~type, ncol = 1,scales = "free")

print(p1)

pdf("../../Plots/Figure4_barplot_DREADD.pdf", height = 2, width = 5.25)
print(p1)
dev.off()

US3$Results[[1]]$Statistics$kmeans.25

cluster_stats <- US3$Results[[1]]$Statistics$kmeans.25
cluster_stats_updated <- cluster_stats[grep("count", cluster_stats$name), ]
cluster_stats_updated$FDR <- p.adjust(cluster_stats_updated$p, method = "BY")
cluster_stats_updated
```


## Behavior flow differences for CRS and DREADD

### CRS

```{r, fig.height=5, fig.width=5}
PlotBehaviorFlow_Delta(US2, grouping = US2$meta$Condition == "Repeated", lab = "kmeans.25")

US2$Results[[1]]$TransitionStats$kmeans.25

trans_stats <- US2$Results[[1]]$TransitionStats$kmeans.25$transitions
trans_stats_updated <- tidyr::drop_na(trans_stats, "p.value")
trans_stats_updated$FDR <- p.adjust(trans_stats_updated$p.value, method = "BY")
trans_stats_updated

pdf("../../Plots/Figure4_behaviorFlow_CRS.pdf", height =5, width = 5)
PlotBehaviorFlow_Delta(US2, grouping = US2$meta$Condition == "Repeated", lab = "kmeans.25")
dev.off()
```

### DREADD

```{r, fig.height=5, fig.width=5}
PlotBehaviorFlow_Delta(US3, grouping = US3$meta$Treatment == "cloz", lab = "kmeans.25")

US3$Results[[1]]$TransitionStats$kmeans.25

trans_stats <- US3$Results[[1]]$TransitionStats$kmeans.25$transitions
trans_stats_updated <- tidyr::drop_na(trans_stats, "p.value")
trans_stats_updated$FDR <- p.adjust(trans_stats_updated$p.value, method = "BY")
trans_stats_updated

pdf("../../Plots/Figure4_behaviorFlow_DREADD.pdf", height =5, width = 5)
PlotBehaviorFlow_Delta(US3, grouping = US3$meta$Treatment == "cloz", lab = "kmeans.25")
dev.off()
```



## BFA for CRS and DREADD

### CRS

```{r, fig.width=4, fig.height=2.5}
PlotTransitionsStats(US2, labels = "kmeans.25")

pdf("../../Plots/Figure4_bootstrapping_CRS.pdf", height = 2.5, width = 4)
PlotTransitionsStats(US2, labels = "kmeans.25")
dev.off()
```

### DREADD

```{r, fig.width=4, fig.height=2.5}
PlotTransitionsStats(US3, labels = "kmeans.25")

pdf("../../Plots/Figure4_bootstrapping_DREADD.pdf", height = 2.5, width = 4)
PlotTransitionsStats(US3, labels = "kmeans.25")
dev.off()
```

## Sensitivity plots for CRS and DREADD

### CRS

```{r,fig.width= 3.5, fig.height=2}
dat <- readRDS("../../data/XXX")

#-log 10 transform statistical values
dat[,-c(1:2)] <- -log10(dat[,-c(1:2)])

#aggregate mean and sd
means <- aggregate(dat, FUN = mean, by = list(dat$n_animals))
sds <- aggregate(dat, FUN = sd, by = list(dat$n_animals))
means <- means[,-c(2:3)]
sds <- sds[,-c(2:3)]

gs <- means$Group.1 / 2
means <- gather(means, key = "Group.1", value = "p.value")
means$GroupSize <- rep(gs,ncol(dat) - 2)
sds <- gather(sds, key = "Group.1", value = "sd")
means$sem <- gather(sds, key = "Group.1", value = "sd")$sd / sqrt(max(dat$n_sim))

#means <- means[means$GroupSize != 25,]
means$Type <- "Classical"
means$Type[grepl("kmeans.",means$Group.1)] <- "kmeans"

p1 <- ggplot(means[means$Group.1 %in% c("kmeans.25.matstats.p","classical.top.p","DLC.PCA.p"),], aes(GroupSize,p.value, color = Group.1)) + 
  geom_ribbon(aes(ymin = p.value-sem,ymax = p.value+sem, fill = Group.1,alpha = 0.1)) + 
  geom_line(size = 1) +
  scale_x_reverse(breaks = gs) + 
  scale_color_manual(values = c("grey","black","#994F88")) +
  scale_fill_manual(values = c("grey","black","#994F88")) +
  #geom_hline(yintercept = -log10(0.05), color = "red") +
  ylim(0.5, 7) +
  theme_bw() + ylab("-log10(p-value)") + xlab("group size") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"))

print(p1)

pdf("../../Plots/Figure4_sensitivity_CRS.pdf", height = 2, width = 3.5)
print(p1)
dev.off()
```


### DREADD

```{r,fig.width= 3.5, fig.height=1.5}
dat <- readRDS("../../data/XXX")

#-log 10 transform statistical values
dat[,-c(1:2)] <- -log10(dat[,-c(1:2)])

#aggregate mean and sd
means <- aggregate(dat, FUN = mean, by = list(dat$n_animals))
sds <- aggregate(dat, FUN = sd, by = list(dat$n_animals))
means <- means[,-c(2:3)]
sds <- sds[,-c(2:3)]

gs <- means$Group.1 / 2
means <- gather(means, key = "Group.1", value = "p.value")
means$GroupSize <- rep(gs,ncol(dat) - 2)
sds <- gather(sds, key = "Group.1", value = "sd")
means$sem <- gather(sds, key = "Group.1", value = "sd")$sd / sqrt(max(dat$n_sim))

#means <- means[means$GroupSize != 25,]
means$Type <- "Classical"
means$Type[grepl("kmeans.",means$Group.1)] <- "kmeans"


p1 <- ggplot(means[means$Group.1 %in% c("kmeans.25.matstats.p","classical.top.p","DLC.PCA.p"),], aes(GroupSize,p.value, color = Group.1)) + 
  geom_ribbon(aes(ymin = p.value-sem,ymax = p.value+sem, fill = Group.1,alpha = 0.1)) + 
  geom_line(size = 1) +
  scale_x_reverse(breaks = gs) + 
  scale_color_manual(values = c("grey","black","#994F88")) +
  scale_fill_manual(values = c("grey","black","#994F88")) +
  #geom_hline(yintercept = -log10(0.05), color = "red") +
  ylim(0.5, 7) +
  theme_bw() + ylab("-log10(p-value)") + xlab("group size") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"))


print(p1)

pdf("../../Plots/Figure4_sensitivity_DREADD.pdf", height = 1.5, width = 3.5)
print(p1)
dev.off()
```


## 2D embeddings for CRS and DREADD

## CRS

```{r, fig.height=2.7, fig.width=3.6}
US2 <- CalculateStabilizedTransitions(US2, group = "Condition",control = "Control",labels = "kmeans.25")
p1 <- Plot2DEmbedding(US2,transitionmatrices_stabilized = "kmeans.25",colorby = "Condition",colors =  c("grey","#009E73"),plot.sem = TRUE, method = "umap", seed = 123)
print(p1)

pdf("../../Plots/Figure4_2Dembedding_CRS.pdf", height = 2.7, width = 3.6)
print(p1)
dev.off()
```

## DREADD

```{r, fig.height=2.7, fig.width=3.38}
US3 <- CalculateStabilizedTransitions(US3, group = "Treatment",control = "saline",labels = "kmeans.25")
p1 <- Plot2DEmbedding(US3,transitionmatrices_stabilized = "kmeans.25",colorby = "Treatment",colors =  c("#E69F00", "grey"),plot.sem = TRUE, method = "umap", seed = 123)
print(p1)

pdf("../../Plots/Figure4_2Dembedding_DREADD.pdf", height = 2.7, width = 3.38)
print(p1)
dev.off()
```


## 2D embedding of all data

```{r, fig.width=5.5, fig.height=3.2}
US_all <- CalculateStabilizedTransitions(US_all,"Condition","Control",subset = US_all$meta$Session == "CRS1")
US_all <- CalculateStabilizedTransitions(US_all,"Condition","Control",subset = US_all$meta$Session == "PostCSI")
US_all <- CalculateStabilizedTransitions(US_all,"Treatment","Control",subset = US_all$meta$Session == "FST45min")
US_all <- CalculateStabilizedTransitions(US_all,"Treatment","Saline",subset = US_all$meta$Session == "PostYoh")
US_all <- CalculateStabilizedTransitions(US_all,"Treatment","saline",subset = US_all$meta$Session == "DREADD")

US_all$meta$Embedding <- "Control"
US_all$meta$Embedding[US_all$meta$Session == "CRS1" & US_all$meta$Condition != "Control"] <- "CRS"
US_all$meta$Embedding[US_all$meta$Session == "PostCSI" & US_all$meta$Condition != "Control"] <- "CSI"
US_all$meta$Embedding[US_all$meta$Session == "FST45min" & US_all$meta$Treatment != "Control"] <- "FST_45min"
US_all$meta$Embedding[US_all$meta$Session == "PostYoh" & US_all$meta$Treatment != "Saline"] <- "Yohimbin"
US_all$meta$Embedding[US_all$meta$Session == "DREADD" & US_all$meta$Treatment != "saline"] <- "DREADD"

p1 <- Plot2DEmbedding(US_all,transitionmatrices_stabilized = "kmeans.25", colorby = "Embedding", colors = c("grey","#009E73","#0072B2","#E69F00", "#D52800", "#CC79A7"), seed = 123,
                      plot.sem = TRUE)
p1

pdf("../../Plots/Figure4_2Dembedding_allDatasets.pdf", height=3.2, width = 5.5)
print(p1)
dev.off()
```
