---
title: "Figure1_kmeans_70Clusters"
author: "Fabienne Rössler"
date: '2023-02-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning = FALSE}
source("../DLCAnalyzer_Functions_v4.R")
source("../UnsupervisedAnalysis_Functions.R")
library(sp)         #tested with v1.3-2
library(imputeTS)   #tested with v2.7
library(ggplot2)    #tested with v3.1.0
library(ggmap)      #tested with v3.0.0
library(data.table) #tested with v1.12.8
library(cowplot)    #tested with v0.9.4
library(corrplot)   #tested with v0.84
library(keras)      #REQUIRES TENSORFLOW INSTALL. tested with v2.2.5.0
library(readr)
library(tidyr)
library(biganalytics)
library(M3C)
library(stringr)
library(reticulate)
set.seed(123)
```

# Figure 1 (for kmeans with 70 clusters)

```{r}
US <- readRDS("../../data/US_ComparisonClustering_CSI_processed.rds")
US <- TwoGroupAnalysis(US, US$meta$Condition, lab = "kmeans.70_CSI")
```

## Boxplots for raw readouts

```{r, fig.height=3.1, fig.width=4}
US_temp <- readRDS("../../data/US_AllData.rds")
US_temp <- SplitUSData(US_temp, select = US_temp$meta$Session %in% c("PostCSI"))

stats <- US_temp$Results$`CSI-vs-Control`$Statistics$raw
pdat <- US_temp$Report$raw

# Repeat multiple testing correction for raw readouts
group <- US_temp$meta$Condition

pdat <- dplyr::select(pdat,!dplyr::contains("kmeans"))

res <- NULL
for(i in names(pdat)){
  a <- pdat[group == unique(group)[1],i]
  b <- pdat[group == unique(group)[2],i]
  nline <- data.frame(i, t.test(a,b)$statistic, t.test(a,b)$parameter, t.test(a,b)$p.value, mean(a), mean(b), mean(a) / mean(b))
  names(nline) <- c("name","t", "df", "p",unique(group)[1], unique(group)[2], "FC")
  res <- rbind(res,nline)
}
res$FDR <- p.adjust(res$p, method = "BY")
stats <- res

stats

pdat <- data.frame(filename = rownames(pdat),pdat)
pdat <- gather(pdat,key = "key",value = "value", -filename)
pdat$value[is.na(pdat$value)] <- 0
assign <- match(pdat$filename, US_temp$meta$filename)
pdat$Group <- US_temp$meta$Condition[assign]

pdat <- pdat[pdat$key %in% c("classifications.Supported.count","classifications.Unsupported.count","bodycentre.center.total.time","bodycentre.distance.moving"),]
p1 <- ggplot(pdat,aes(Group,value, color = Group)) + 
  geom_boxplot(outlier.shape = NA) + 
  scale_color_manual(values = c("black","#0072B2")) + 
  geom_point(position = position_jitter(width = 0.15)) + 
  facet_wrap(~key, scales = "free") + 
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank())
 
stats[stats$name %in% c("classifications.Supported.count","classifications.Unsupported.count","bodycentre.center.total.time","bodycentre.distance.moving"),]

print(p1)

pdf("../../Plots/Figure1_classicalReadouts_boxplot.pdf", height = 3.1, width = 4)
print(p1)
dev.off()
```

## Barplot for occurence of different clusters

```{r, fig.height=1.5, fig.width=11}
pdat <- US$Report$kmeans.70_CSI
pdat <- data.frame(filename = rownames(pdat),pdat)
pdat <- gather(pdat,key = "key",value = "value", -filename)
pdat$value[is.na(pdat$value)] <- 0
pdat$type <- unlist(lapply(pdat$key,FUN = function(x){strsplit(x, split = "\\.")[[1]][2]}))
pdat$Cluster <- unlist(lapply(pdat$key,FUN = function(x){strsplit(x, split = "\\.")[[1]][1]}))
pdat$Cluster <- as.integer(unlist(lapply(pdat$Cluster,FUN = function(x){strsplit(x, split = "X")[[1]][2]})))
assign <- match(pdat$filename, US$meta$filename)
pdat$Group <- US$meta$Condition[assign]
pdat$value <- ifelse(pdat$type == "nframes",pdat$value / 70, pdat$value)
pdat$type[pdat$type == "nframes"] <- "time"
pdat <- pdat[pdat$type == "count",]
df <- aggregate(pdat$value,by = list(pdat$Cluster, pdat$type, pdat$Group), FUN = mean)
colnames(df) <- c("Cluster","type","Group","Mean")
df$SEM <- aggregate(pdat$value,by = list(pdat$Cluster, pdat$type, pdat$Group), FUN = sd)$x / sqrt(30)


p1 <- ggplot(df, aes(x=Cluster, y=Mean, fill=Group, width = 0.75)) + 
  geom_bar(stat="identity", color="black", 
           position=position_dodge()) +
  scale_fill_manual(values = c("white","#0072B2")) +
  geom_errorbar(aes(ymin=Mean-SEM, ymax=Mean+SEM), width=.2,
                position=position_dodge(.8)) +
  #geom_point(data = pdat, aes(Cluster, value, color = Group), position = position_jitterdodge(.3), color = "black", alpha = 0.2, size = 0.3)+ 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
  scale_x_continuous(breaks = c(1:70)) +
  facet_wrap(~type, ncol = 1,scales = "free")

print(p1)

pdf("../../Plots/Figure1_kmeans70_barplot.pdf", height = 1.5, width = 11)
print(p1)
dev.off()

US$Results[[1]]$Statistics$kmeans.70_CSI

cluster_stats <- US$Results[[1]]$Statistics$kmeans.70_CSI
cluster_stats_updated <- cluster_stats[grep("count", cluster_stats$name), ]
cluster_stats_updated$FDR <- p.adjust(cluster_stats_updated$p, method = "BY")
cluster_stats_updated
```

## Circle plots for transitions between clusters

```{r, fig.height=5, fig.width=5}
PlotBehaviorFlow(US,lab = "kmeans.70_CSI")

pdf("../../Plots/Figure1_kmeans70_circlePlot.pdf", height = 5, width = 5)
PlotBehaviorFlow(US,lab = "kmeans.70_CSI")
dev.off()
```


## Results of bootstrapping analysis

```{r, fig.width= 4.8, fig.height=1.6}
PlotTransitionsStats(US, labels = "kmeans.70_CSI")

pdf("../../Plots/Figure1_bootstrapping_kmeans70.pdf", height = 1.6, width = 4.8)
PlotTransitionsStats(US, labels = "kmeans.70_CSI")
dev.off()
```


## Results of sensitivity analysis

Plot for comparison between different clustering algorithms:

```{r,fig.width= 3.2, fig.height=1.7}
dat <- readRDS("../../data/XXX")

dat[dat == 0] <- min(dat[dat != 0])

#-log 10 transform statistical values
dat[,-c(1:2)] <- -log10(dat[,-c(1:2)])

#aggregate mean and sd
means <- aggregate(dat, FUN = mean, by = list(dat$n_animals))
sds <- aggregate(dat, FUN = sd, by = list(dat$n_animals))
means <- means[,-c(2:3)]
sds <- sds[,-c(2:3)]

gs <- means$Group.1 / 2
means <- gather(means, key = "Group.1", value = "p.value")
means$GroupSize <- rep(gs,ncol(dat) - 2)
sds <- gather(sds, key = "Group.1", value = "sd")
means$sem <- gather(sds, key = "Group.1", value = "sd")$sd / sqrt(max(dat$n_sim))

means$Type <- "Classical"
means$Type[grepl("kmeans.",means$Group.1)] <- "kmeans"
means$Type[grepl("BSOID.",means$Group.1)] <- "BSOID"
means$Type[grepl("VAME.",means$Group.1)] <- "VAME"
means_CSI <- means

#p1 <- ggplot(means[means$Group.1 %in% c("kmeans.70.matstats.p","BSOID.8.matstats.p","VAME.80.matstats.p","classical.top.p","DLC.PCA.p"),], aes(GroupSize,p.value, color = Group.1)) +
p1 <- ggplot(means[means$Group.1 %in% c("kmeans.70.matstats.p","classical.top.p","DLC.PCA.p"),], aes(GroupSize,p.value, color = Group.1)) +
  geom_ribbon(aes(ymin = p.value-sem,ymax = p.value+sem, fill = Group.1,alpha = 0.1)) + 
  geom_line(size = 1) +
  ylim(0.3, 9.3) +
  scale_x_reverse() + 
  scale_color_manual(values = c("grey","black","#994F88")) +
  scale_fill_manual(values = c("grey","black","#994F88")) +
  #geom_hline(yintercept = -log10(0.05), color = "red") +
  theme_bw() + ylab("-log10(p-value)") + xlab("group size") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"))

print(p1)

pdf("../../Plots/Figure1_SensitivityCurves_comparison.pdf", height = 1.7, width = 3.37)
print(p1)
dev.off()
```

Plot for comparing different cluster numbers:

```{r,fig.width= 3.37, fig.height=1.7}
p1 <- ggplot(means[means$Group.1 %in% c("kmeans.10.matstats.p","kmeans.25.matstats.p","kmeans.70.matstats.p", "kmeans.100.matstats.p","classical.top.p","DLC.PCA.p"),], 
             aes(GroupSize,p.value, color = Group.1)) + 
  geom_ribbon(aes(ymin = p.value-sem,ymax = p.value+sem, fill = Group.1,alpha = 0.1)) + 
  geom_line(size = 1) +
  scale_x_reverse() + 
  ylim(0.3, 9.3) +
  scale_color_manual(values = c("grey","black", "#D5B9D1","#511B44","#B27CA6", "#8A487A")) +
  scale_fill_manual(values = c("grey","black", "#D5B9D1","#511B44","#B27CA6", "#8A487A")) +
  #(yintercept = -log10(0.05), color = "red") +
  theme_bw() + ylab("-log10(p-value)") + xlab("group size") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"))

print(p1)

pdf("../../Plots/Figure1_SensitivityCurves_diffNumClusters.pdf", height = 1.7, width = 3.39)
print(p1)
dev.off()
```


Plot for different integration periods:

```{r,fig.width= 3.43, fig.height=1.7}
p1 <- ggplot(means[means$Group.1 %in% c("kmeans.70.5.matstats.p","kmeans.70.10.matstats.p","kmeans.70.matstats.p", "kmeans.70.30.matstats.p","classical.top.p","DLC.PCA.p"),], 
             aes(GroupSize,p.value, color = Group.1)) + 
  geom_ribbon(aes(ymin = p.value-sem,ymax = p.value+sem, fill = Group.1,alpha = 0.1)) + 
  geom_line(size = 1) +
  scale_x_reverse() +
  ylim(0.3, 9.3) +
  scale_color_manual(values = c("grey","black", "#6F9FD3","#114375","#A5C9E9", "#35669B")) +
  scale_fill_manual(values = c("grey","black", "#6F9FD3","#114375","#A5C9E9", "#35669B")) +
  #geom_hline(yintercept = -log10(0.05), color = "red") +
  theme_bw() + ylab("-log10(p-value)") + xlab("group size") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"))

print(p1)

pdf("../../Plots/Figure1_SensitivityCurves_diffIntegrationPeriod.pdf", height = 1.7, width = 3.47)
print(p1)
dev.off()
```