---
title: "ClusterClassifier_AllData_25Clusters"
author: "Fabienne Rössler"
date: '2023-06-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning = FALSE}
source("DLCAnalyzer_Functions_v4.R")
source("UnsupervisedAnalysis_Functions.R")
library(sp)         #tested with v1.3-2
library(imputeTS)   #tested with v2.7
library(ggplot2)    #tested with v3.1.0
library(ggmap)      #tested with v3.0.0
library(data.table) #tested with v1.12.8
library(cowplot)    #tested with v0.9.4
library(corrplot)   #tested with v0.84
library(keras)      #REQUIRES TENSORFLOW INSTALL. tested with v2.2.5.0
library(readr)
library(tidyr)
library(biganalytics)
library(M3C)
set.seed(123)
```

# Apply cluster classifier for k-means with 25 cluster to all datasets (CSI, AS, yohimbine, CRS, DREADD) 

Process all files using the cluster classifier for k-means with 25 clusters.

```{r, eval = FALSE}
model_kmeans25 <- load_model_hdf5("../kmeans_classifiers/kmeans.25.model.hdf5")
model_kmeans25_para <- readRDS("../kmeans_classifiers/kmeans.25.model.PARAMETERS.rds")

pipeline <- function(path){
  Tracking <- ReadDLCDataFromCSV(path, fps = 25)
  Tracking$data$centre <- NULL
  Tracking <- CutTrackingData(Tracking,start = 300,end = 300)
  Tracking <- CalibrateTrackingData(Tracking, "area",in.metric = 42*42, c("tr","tl","bl","br"))
  Tracking <- AddOFTZones(Tracking)
  Tracking <- CleanTrackingData(Tracking, likelihoodcutoff = 0.95, existence.pol = ScalePolygon(Tracking$zones$arena,1.3))
  Tracking <- CalculateAccelerations(Tracking)
  Tracking <- CreateSkeletonData_OFT_v4(Tracking)
  Tracking <- ZscoreNormalizeFeatures(Tracking,omit =names(Tracking$features)[c(1:23)],type = "mean")
  Tracking$features <- ScaleFeatures(Tracking$features, select = names(Tracking$features)[1:11], factor = 4)
  Tracking$features <- ScaleFeatures(Tracking$features, select = names(Tracking$features)[20:23], factor = 0.1)
  
  Tracking <- ClassifyBehaviors(Tracking, model_kmeans25, model_kmeans25_para)
  Tracking$labels$kmeans.25 <- Tracking$labels$classifications
  
  Tracking$labels$classifications <- NULL
  Tracking$train_x <- NULL
  return(Tracking)
}

# We need a different pipeline for DREADD as the files contain 20 min of recording (we only use the first 10 min)
pipeline_DREADD <- function(path){
  Tracking <- ReadDLCDataFromCSV(path, fps = 25)
  Tracking$data$centre <- NULL
  Tracking <- CutTrackingData(Tracking,start = 300,end = 15000)
  Tracking <- CalibrateTrackingData(Tracking, "area",in.metric = 42*42, c("tr","tl","bl","br"))
  Tracking <- AddOFTZones(Tracking)
  Tracking <- CleanTrackingData(Tracking, likelihoodcutoff = 0.95, existence.pol = ScalePolygon(Tracking$zones$arena,1.3))
  Tracking <- CalculateAccelerations(Tracking)
  Tracking <- CreateSkeletonData_OFT_v4(Tracking)
  Tracking <- ZscoreNormalizeFeatures(Tracking,omit =names(Tracking$features)[c(1:23)],type = "mean")
  Tracking$features <- ScaleFeatures(Tracking$features, select = names(Tracking$features)[1:11], factor = 4)
  Tracking$features <- ScaleFeatures(Tracking$features, select = names(Tracking$features)[20:23], factor = 0.1)
  
  Tracking <- ClassifyBehaviors(Tracking, model_kmeans25, model_kmeans25_para)
  Tracking$labels$kmeans.25 <- Tracking$labels$classifications
  
  Tracking$labels$classifications <- NULL
  Tracking$train_x <- NULL
  return(Tracking)
}


#CSI data
path <- "../data/CSI_SA/"
files <- grep(pattern = ".csv",list.files(path),value = TRUE)
ts <- RunPipeline(files,path,pipeline)

#FST data
path <- "../data/AS/"
files <- grep(pattern = ".csv",list.files(path),value = TRUE)
ts <- append(ts,RunPipeline(files,path,pipeline))


#Yohimbin data
path <- "../data/Yohimbine/"
files <- grep(pattern = ".csv",list.files(path),value = TRUE)
ts <- append(ts,RunPipeline(files,path,pipeline))

#DREADD data
path <- "../data/DREADD/"
files <- grep(pattern = ".csv",list.files(path),value = TRUE)
ts_transfer <- RunPipeline(files,path,pipeline_DREADD)

#CRS data
path <- "../data/CRS/"
files <- grep(pattern = ".csv",list.files(path),value = TRUE)
ts_transfer <- append(ts_transfer,RunPipeline(files,path,pipeline))


for(i in names(ts)){
  ts[[i]]$train_x <- NULL
}

for(i in names(ts_transfer)){
  ts_transfer[[i]]$train_x <- NULL
}

```

We then create an unsupervised analysis dataobject. We add the metadata that contains the experimental details and save it as one object.

```{r, eval = FALSE}
US_transfer <- LoadFromTrackingObject(append(ts,ts_transfer))
meta_transfer <- read.table("../metadata/AllData_25Clusters.csv", sep = ";", header = T)
rownames(meta_transfer) <- meta_transfer$DLCFile
meta_transfer$DLCFile <- NULL

US_transfer <- AddMetaData(US_transfer, meta_transfer)

saveRDS(US_transfer,"../data/US_AllData_25Clusters.rds")
saveRDS(append(ts, ts_transfer), "../data/TS_AllData_25Clusters.rds.rds")
```

## Pre-processing the data

We load the data for the unsupervised analysis object.

```{r}
US <- readRDS("../data/US_AllData_25Clusters.rds")
```

We first smooth the data over 5 frames, this removes clusters that were identified in a single frame and ensures that behavior trains are better resolved.

```{r, eval = FALSE}
US <- SmoothLabels_US(US, 5)
```

We calculate metrics, such as number of onset-offset and number of frames for each cluster.

```{r, eval = FALSE}
US <- CalculateMetrics(US)
```

Next, we calculate the transition matrix for each clustering analysis in each file.

```{r, eval = FALSE}
US <- AddTransitionMatrixData(US)
```

We save this object, so next time we do not have to re-process it.

```{r, eval = FALSE}
saveRDS(US,"../data/US_AllData_25Clusters.rds")
```