---
title: "CRS1_LDB_Clustering"
author: "Lukas von Ziegler"
date: '2024-01-26'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message=FALSE, warning = FALSE}
source("DLCAnalyzer.R")
source("BFA_BFF.R")
library(sp)         #tested with v1.3-2
library(imputeTS)   #tested with v2.7
library(ggplot2)    #tested with v3.1.0
library(ggmap)      #tested with v3.0.0
library(data.table) #tested with v1.12.8
library(cowplot)    #tested with v0.9.4
library(corrplot)   #tested with v0.84
library(keras)      #REQUIRES TENSORFLOW INSTALL. tested with v2.2.5.0
library(readr)
library(tidyr)
library(biganalytics)
library(M3C)
set.seed(123)
```



# CRS1 LDB

In this document we perform a clustering on LDB samples from the CRS1 experiment

Again, first we define our pipeline

```{r, eval = FALSE}
zoneinfo <- read.table("../metadata_revision/LDB_zoneinfo.csv", sep = ";", header = T)

pipeline <- function(path){
  Tracking <- ReadDLCDataFromCSV(path, fps = 25)
  Tracking <- CleanTrackingData(Tracking, likelihoodcutoff = 0.95)
  Tracking <- CalibrateTrackingData(Tracking, method = "area",in.metric = 30*(15.7+28), points = c("tl","tr","br","bl"))
  Tracking <- AddZones(Tracking,zoneinfo)
  Tracking <- CalculateAccelerations(Tracking)
  Tracking <- CreateSkeletonData_LDB_v2(Tracking)
  Tracking <- ZscoreNormalizeFeatures(Tracking,omit = names(Tracking$features)[c(1:23)],type = "mean")
  Tracking$features <- ScaleFeatures(Tracking$features, select = names(Tracking$features)[1:11], factor = 4)
  Tracking$features <- ScaleFeatures(Tracking$features, select = names(Tracking$features)[20:23], factor = 0.1)
  Tracking <- LDBAnalysis(Tracking,5 ,5, points = "bodycentre")
  Tracking <- CreateTestSet(Tracking, integration_period = 15)
  return(Tracking)
}
```


```{r, eval = FALSE}
# data
path <- "../data/XXX/"
files <- grep(pattern = ".csv",list.files(path),value = TRUE)
ts <- RunPipeline(files,path,pipeline)
```

we are now ready to run the unsupervised clustering. we use kmeans on the sequence data.

```{r, eval = FALSE}
centers <- c(25)

for(i in centers){
  ts <- UnsupervisedClusteringKmeans(ts, N_clusters = i,Z_score_Normalize = TRUE)
  for(j in names(ts)){
    ts[[j]]$labels[[paste("kmeans",i,sep = ".")]] <- ts[[j]]$labels$unsupervised
    ts[[j]]$labels$unsupervised <- NULL
  }
}
```


save the data

```{r, eval = FALSE}
ts2 <- ts
for(i in names(ts2)){
  ts2[[i]]$train_x <- NULL
}
saveRDS(ts2,"../data/TS_CRS1_LDB.rds")
```



```{r, eval = FALSE}
ts <- readRDS("../data/TS_CRS1_LDB.rds")
for(i in names(ts[[1]]$labels)){
  print(paste("creating training set for:",i, sep = " "))
  for(j in names(ts)){
    ts[[j]] <- CreateTrainingSet(ts[[j]], integration_period = 15, label.group = i)
  }
  
  MLData <- CombineTrainingsData(ts,shuffle = TRUE)

#initialize model
model <- keras_model_sequential() 
model %>% 
  layer_dense(units = 1024, activation = 'relu', input_shape = c(MLData$parameters$N_input),kernel_regularizer = regularizer_l2(l = 0)) %>% 
  layer_dropout(rate = 0.4) %>% 
  layer_dense(units = MLData$parameters$N_features, activation = 'softmax')

#define optimizer
model %>% compile(
  loss = 'categorical_crossentropy',
  optimizer = optimizer_rmsprop(),
  metrics = c('accuracy')
)

#train model
history <- model %>% fit(
  MLData$train_x, MLData$train_y, 
  epochs = 30, batch_size = 512, 
  validation_split = 0
)

save_model_hdf5(model,paste("../kmeans_classifiers_revision/",i,"_LDB.model.hdf5", sep = ""))
saveRDS(MLData$parameters,file = paste("../kmeans_classifiers_revision/",i,"_LDB.model.PARAMETERS.rds", sep = ""))
}
```


Next we use the function LoadFromTrackingObject to create a USData object. we add the metadata that contains the experimental details and save it as one object

```{r, eval = FALSE}
US <- LoadFromTrackingObject(ts)
meta <- read.table("../metadata_revision/metadata_CRS1_LDB.csv", sep = ";", header = T)
rownames(meta) <- meta$DLCFile
meta$DLCFile <- NULL

US <- AddMetaData(US, meta)
US <- SmoothLabels_US(US, 5)
US <- CalculateMetrics(US)
US <- AddTransitionMatrixData(US)

saveRDS(US,"../data_revision/US_CRS1_LDB.rds")
```