---
title: "ResilientPhenotype_IFS"
author: "Fabienne Rössler"
date: '2023-04-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning = FALSE}
source("DLCAnalyzer_Functions_v4.R")
source("UnsupervisedAnalysis_Functions.R")
library(rlang)
library(sp)         #tested with v1.3-2
library(imputeTS)   #tested with v2.7
library(ggplot2)    #tested with v3.1.0
library(ggmap)      #tested with v3.0.0
library(data.table) #tested with v1.12.8
library(cowplot)    #tested with v0.9.4
library(corrplot)   #tested with v0.84
library(keras)      #REQUIRES TENSORFLOW INSTALL. tested with v2.2.5.0
library(readr)
library(tidyr)
library(biganalytics)
library(M3C)
library(stringr)
library(reticulate)
library(pROC)
library(yardstick)
library(rhdf5)
set.seed(123)
```

# Categorize stressed animals into resilient and susceptible based on 2D embedding (UMAP)

Load US object for IFS experiment.

```{r}
US <- readRDS("../data/US_IFS_25Clusters_processed.rds")

US2 <- SplitUSData(US, select = US$meta$Session %in% c("OFT2"))
```

To define resilient and susceptible animals, we use the UMAP1 and UMAP2 coordinates of the 2D embeddings. We then define a function to find the best separating threshold between stressed and control animals for both coordinates.  

```{r}
setThreshold <- function(p) {
  p$data$col <- as.factor(p$data$col)
  
  roc_X1 <- roc(p$data, response = col, predictor = X1)
  ind_thres_x1 <- which.max(sqrt(roc_X1$sensitivities*roc_X1$specificities))
  thres_x1 <- roc_X1$thresholds[ind_thres_x1]
  
  roc_X2 <- roc(p$data, response = col, predictor = X2)
  ind_thres_x2 <- which.max(sqrt(roc_X2$sensitivities*roc_X2$specificities))
  thres_x2 <- roc_X2$thresholds[ind_thres_x2]

  thres <- NULL
  thres$X1 <- thres_x1
  thres$X2 <- thres_x2
  
  return(thres)
}
```

We then search for the best separating thresholds several times, each time for a different random seed. This way the grouping into resilient and susceptible animals is more robust towards changing the random seed. 

```{r}
int_runs <- 101

set.seed(123)
list_seeds <- sample.int(10000, int_runs)
groups_diffSeeds <- US2$meta[ , c("animal_ID", "group")]
for (i in list_seeds) {
  p1 <- Plot2DEmbedding(US2,transitionmatrices = "kmeans.25",colorby = "group", colors =  c("grey","red"), plot.sem = TRUE, method = "umap", seed = i)

  curr_thres <- setThreshold(p1)
  
  p2 <- Plot2DEmbedding(US2,transitionmatrices = "kmeans.25",colorby = "animal_ID", colors =  c("grey","red"), plot.sem = TRUE, method = "umap", seed = i)

  # Count number of TFS animals in each quadrant 
  num_animals <- replicate(4, 0)
  num_animals[1] <- length(p1$data$col[p1$data$X1 < curr_thres$X1 & p1$data$X2 >= curr_thres$X2 & p1$data$col == 'TFS'])
  num_animals[2] <- length(p1$data$col[p1$data$X1 >= curr_thres$X1 & p1$data$X2 >= curr_thres$X2 & p1$data$col == 'TFS'])
  num_animals[3] <- length(p1$data$col[p1$data$X1 >= curr_thres$X1 & p1$data$X2 < curr_thres$X2 & p1$data$col == 'TFS'])
  num_animals[4] <- length(p1$data$col[p1$data$X1 < curr_thres$X1 & p1$data$X2 < curr_thres$X2 & p1$data$col == 'TFS'])
  
  ind_quadrant <- which.max(num_animals)
  if (ind_quadrant == 1) {
    ID_nonres <- p2$data$col[p1$data$X1 < curr_thres$X1 & p1$data$X2 >= curr_thres$X2 & p1$data$col == 'TFS']
    ID_res <- p2$data$col[(p1$data$X1 >= curr_thres$X1 | p1$data$X2 < curr_thres$X2) & p1$data$col == 'TFS']
  } else if (ind_quadrant == 2) {
    ID_nonres <- p2$data$col[p1$data$X1 >= curr_thres$X1 & p1$data$X2 >= curr_thres$X2 & p1$data$col == 'TFS']
    ID_res <- p2$data$col[(p1$data$X1 < curr_thres$X1 | p1$data$X2 < curr_thres$X2) & p1$data$col == 'TFS']
  } else if (ind_quadrant == 3) {
    ID_nonres <- p2$data$col[p1$data$X1 >= curr_thres$X1 & p1$data$X2 < curr_thres$X2 & p1$data$col == 'TFS']
    ID_res <- p2$data$col[(p1$data$X1 < curr_thres$X1 | p1$data$X2 >= curr_thres$X2) & p1$data$col == 'TFS']
  } else if (ind_quadrant == 4) {
    ID_nonres <- p2$data$col[p1$data$X1 < curr_thres$X1 & p1$data$X2 < curr_thres$X2 & p1$data$col == 'TFS']
    ID_res <- p2$data$col[(p1$data$X1 >= curr_thres$X1 | p1$data$X2 >= curr_thres$X2) & p1$data$col == 'TFS']
  }

  groups_diffSeeds <- cbind(groups_diffSeeds, res_ID = "control")
  groups_diffSeeds[groups_diffSeeds$animal_ID %in% ID_nonres, ncol(groups_diffSeeds)] <- "susceptible"
  groups_diffSeeds[groups_diffSeeds$animal_ID %in% ID_res, ncol(groups_diffSeeds)] <- "resilient"
}


# Count categorization of each animal as either resilient or susceptible
groups_diffSeeds$num_resilient <- NULL
groups_diffSeeds$num_resilient <- rowSums(groups_diffSeeds[ , 3:(2+int_runs)] == "resilient")/int_runs
groups_diffSeeds$num_susceptible <- NULL
groups_diffSeeds$num_susceptible <- rowSums(groups_diffSeeds[ , 3:(2+int_runs)] == "susceptible")/int_runs
```

Each stressed animal then gets either the class "resilient" or "susceptible" assigned (based on majority vote). We add this information to the meta data and save the US object.

```{r}
temp_meta <- cbind(US2$meta, resilient_ID = "control")
temp_meta[groups_diffSeeds$num_susceptible>0.5, ncol(temp_meta)] <- "susceptible"
temp_meta[groups_diffSeeds$num_resilient>0.5, ncol(temp_meta)] <- "resilient"

temp_meta$perc_resilient <- NULL
temp_meta$perc_resilient <- groups_diffSeeds$num_resilient

meta_all <- US$meta
assign <- match(meta_all$animal_ID, temp_meta$animal_ID)
meta_all$resilient_ID <- temp_meta$resilient_ID[assign]
meta_all$perc_resilient <- temp_meta$perc_resilient[assign]

US$meta <- meta_all

saveRDS(US,"../data/US_IFS_25Clusters_withResilience.rds")
```


